---
title: "leaflet2"
author: "Matt"
date: "7/19/2020"
output: html_document
---

```{r}
library(tidyverse)
library(leaflet)
```

```{r}

# first 20 quakes
df.20 <- quakes[1:20,]

getColor <- function(quakes) {
  sapply(quakes$mag, function(mag) {
  if(mag <= 4) {
    "green"
  } else if(mag <= 5) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(df.20)
)

leaflet(df.20) %>% addTiles() %>%
  addAwesomeMarkers(~long, ~lat, icon=icons, label=~as.character(mag))
```

The library argument has to be one of ‘ion’, ‘fa’, or ‘glyphicon’. The icon argument needs to be the name of any valid icon supported by the the respective library (w/o the prefix of the library name).

### Marker Clusters
When there are a large number of markers on a map, you can cluster them using the Leaflet.markercluster plug-in. To enable this plug-in, you can provide a list of options to the argument clusterOptions, e.g.

```{r}
leaflet(quakes) %>% addTiles() %>% addMarkers(
  clusterOptions = markerClusterOptions()
)
```

Using the freezeAtZoom argument of the markerClusterOptions() function you can set the clustering to freeze as a specific zoom level. For example markerClusterOptions(freezeAtZoom = 5) will freeze the cluster at zoom level 5 regardless of the user’s actual zoom level.

### Circle Markers
Circle markers are much like regular circles (see Lines and Shapes), except that their radius in onscreen pixels stays constant regardless of zoom level.

You can use their default appearance:
```{r}
df <- sp::SpatialPointsDataFrame(
  cbind(
    (runif(20) - .5) * 10 - 90.620130,  # lng
    (runif(20) - .5) * 3.8 + 25.638077  # lat
  ),
  data.frame(type = factor(
    ifelse(runif(20) > 0.75, "pirate", "ship"),
    c("ship", "pirate")
  ))
)
leaflet(df) %>% addTiles() %>% addCircleMarkers()
```

```{r}
# Create a palette that maps factor levels to colors
pal <- colorFactor(c("navy", "red"), domain = c("ship", "pirate"))

leaflet(df) %>% addTiles() %>%
  addCircleMarkers(
    radius = ~ifelse(type == "ship", 6, 10),
    color = ~pal(type),
    stroke = FALSE, fillOpacity = 0.5
  )
```

# Popups

Popups are small boxes containing arbitrary HTML, that point to a specific point on the map.

Use the addPopups() function to add standalone popup to the map.

```{r}
content <- paste(sep = "<br/>",
  "<b><a href='http://www.samurainoodle.com'>Samurai Noodle</a></b>",
  "606 5th Ave. S",
  "Seattle, WA 98138"
)

leaflet() %>% addTiles() %>%
  addPopups(-122.327298, 47.597131, content,
    options = popupOptions(closeButton = FALSE)
  )
```


```{r}
library(htmltools)

df <- read.csv(textConnection(
"Name,Lat,Long
Samurai Noodle,47.597131,-122.327298
Kukai Ramen,47.6154,-122.327157
Tsukushinbo,47.59987,-122.326726"
))

leaflet(df) %>% addTiles() %>%
  addMarkers(~Long, ~Lat, popup = ~htmlEscape(Name))
```
In the preceding example, htmltools::htmlEscape was used to santize any characters in the name that might be interpreted as HTML. While it wasn’t necessary for this example (as the restaurant names contained no HTML markup), doing so is important in any situation where the data may come from a file or database, or from the user.

In addition to markers you can also add popups on shapes like lines, circles and other polygons.

# Labels
A label is a textual or HTML content that can attached to markers and shapes to be always displayed or displayed on mouse over. Unlike popups you don’t need to click a marker/polygon for the label to be shown.

```{r}
library(htmltools)

df <- read.csv(textConnection(
"Name,Lat,Long
Samurai Noodle,47.597131,-122.327298
Kukai Ramen,47.6154,-122.327157
Tsukushinbo,47.59987,-122.326726"))

leaflet(df) %>% addTiles() %>%
  addMarkers(~Long, ~Lat, label = ~htmlEscape(Name))
```

Customizing Marker Labels
You can customize marker labels using the labelOptions argument of the addMarkers function. The labelOptions argument can be populated using the labelOptions() function. If noHide is false (the default) then the label is displayed only when you hover the mouse over the marker; if noHide is set to true then the label is always displayed
```{r}
# Change Text Size and text Only and also a custom CSS
leaflet() %>% addTiles() %>% setView(-118.456554, 34.09, 13) %>%
  addMarkers(
    lng = -118.456554, lat = 34.105,
    label = "Default Label",
    labelOptions = labelOptions(noHide = T)) %>%
  addMarkers(
    lng = -118.456554, lat = 34.095,
    label = "Label w/o surrounding box",
    labelOptions = labelOptions(noHide = T, textOnly = TRUE)) %>%
  addMarkers(
    lng = -118.456554, lat = 34.085,
    label = "label w/ textsize 15px",
    labelOptions = labelOptions(noHide = T, textsize = "15px")) %>%
  addMarkers(
    lng = -118.456554, lat = 34.075,
    label = "Label w/ custom CSS style",
    labelOptions = labelOptions(noHide = T, direction = "bottom",
      style = list(
        "color" = "red",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )))
```

You can create labels without the accompanying markers using the addLabelOnlyMarkers function.

```{r}
library(rgdal)
library(tidyverse)
# From http://data.okfn.org/data/datasets/geo-boundaries-world-110m
countries <- readOGR("json/countries.geojson")
```

